SNIK Quiz: Automatic Generation of Multiple Choice Questionnaires about Information Management in Hospitals

### 2022-01-21 quiz.tex
Add initial SNIK Quiz paper draft.

%\pretitle{Pretitle}
\title{SNIK: Textbook Knowledge on Hospital Information Management as Linked Data}
%\thanks{This work is supported by the DFG (German Research Foundation) under the Project SNIK, Grant no. 1605/7-1 and 1387/8-1.}%bug: will create an empty first page

@@

\author[A]{\fnms{Konrad} \snm{Höffner}%
%\thanks{Corresponding author: Konrad Höffner, Institute for Medical Informatics, Statistics and Epidemiology, Leipzig University,
\thanks{Corresponding author: Konrad Höffner, IMISE, Leipzig University,
Härtelstraße 16--18, 04107 Leipzig, Germany; E-mail: konrad.hoeffner@imise.uni-leipzig.de.}},
\author[A]{\fnms{Franziska} \snm{Jahn}},
\author[A]{\fnms{Birgit} \snm{Schneider}},
\author[A]{\fnms{Thomas} \snm{Pause}},
\author[A]{\fnms{Alfred} \snm{Winter}}
\runningauthor{K. Höffner et al.}
%\address[A]{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), Leipzig University, Germany}
\address[A]{IMISE, Leipzig University, Germany}
%Medical Informatics, Management of Health Information Systemsi
%Härtelstraße 16--18, D-04107 Leipzig

\iffalse
\author{\IEEEauthorblockN{Konrad Höffner}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-7358-3217}}
\and
\IEEEauthorblockN{Franziska Jahn}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0002-7687-8544}}
\and
\and
\IEEEauthorblockN{Alfred Winter}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
%alfred.winter@imise.uni-leipzig.de}
\url{https://orcid.org/0000-0003-0179-954X}}
\and
\IEEEauthorblockN{Thomas Pause}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-5832-4890}}
}
\fi
\begin{abstract}
%Textbooks contain abstract knowledge about a domain.
Textbooks about information management in hospitals describe the planning, monitoring and directing of a hospital's information system.
SNIK consists of the manually transformed content of three such textbooks as Linked Open Data.
The data model describes information management functions, roles executing these functions and the information used or updated by these functions.
%SNIK provides applications that are used to teach students internationally.
%and the result of applying the data model to three textbooks, an interview and a standard.
%To compare, 
%, making it a natural fit for RDF, RDFS and OWL.
%As the domain is large and highly relevant to students of Medical Informatics, modelling the knowledge is not only possible but also very useful.
We publish the result over several interfaces that are useful for researchers, administrators or students, depending on their objectives and capabilities.
\end{abstract}

@@

\section{Introduction}
A health information system (HIS) is the socio-technical subsystem of a care delivery organization~\citep{bb}.
This includes its different application systems, computers, and network components as well as their users.
A HIS processes data, information, and knowledge and its management involves planning, monitoring and directing those activities.
Due to the complexity and the unique conditions in health care, HIS management is an challenging task.
There are many different frameworks, textbooks and articles describing the scope of HIS management from the perspective of medical informatics.
%However, the disciplines of business informatics and information systems (IS) provide an even broader view on information systems and their management.
%A structured representation of the different perspectives leads to a holistic view on HIS management and helps help researchers and students connect their existing knowledge with further knowledge from other sources during research and learning.
In order to integrate different knowledge sources and to provide the knowledge in a structured, machine-readable data format, we extracted knowledge about HIS management from several sources.%, see \cref{tab:source}.
%three textbooks~\citep{bb,ob,he} and other sources, see \cref{tab:source}.
%\section{Sources}\label{sec:sources}
Three textbooks provide different views on the domain of Hospital Information Management:
\citet{bb} presents a broad view on \enquote{typical architectures of health information systems and their systematic strategic management}.
\citep{ob} concentrates on the \emph{tactical} management of information systems in general and on healthcare in particular.
The focus of tactical management lies on the planning and operation of projects.
\citet{he} explains information management beyond the scope of healthcare.
Other sources are interviews and standards.
%CIOX is based on an interview with the CIO of the Universitätsklinikum Leipzig.
%IT4IT is based on the IT4IT standard.\todo{Sebastian: Was über Standards und IT4IT schreiben}
%
The combination of this knowledge~\citep{semantischesnetz,domaene,approachtosupport} results in SNIK, the Semantic Network of Information Management in Hospitals (\enquote{Krankenhaus} in German).

In order to encourage and enable other researchers, students and health informatics professionals to use available knowledge of HIS management, we introduce different user interfaces to the SNIK ontology and discuss their suitability for different use cases of the target audiences.
%We discuss advantages and disadvantages of the interfaces and give recommendations on which ones present the best compromise for different use cases and target audiences.
%We conclude with plans for future work on interlinking and visualization.

%As the domain is large and highly relevant to students of Medical Informatics, modelling the knowledge is not only possible but also very useful.
Medical informatics students, who are trained for executive positions in information management departments of healthcare institutions, such as hospitals, need a clear terminology of their domain.
Due to different frameworks and textbooks dealing with information management in healthcare, modelling the knowledge unravels the links between the different views on information management.
These are only implicitly known or not known at all by experts in the field.
%
We present a common data model for the domain and the result of applying the data model to three textbooks.
We publish the result over several interfaces that are useful for researchers, practitioners and students, depending on their objectives and their Semantic Web skills.
%
Publishing textbook knowledge as Linked Data enables different ways of teaching.
%The data is continously revised: users constantly report wrong or missing data in the visualization, which is then corrected, respectively revised, by the researchers of the project.

\begin{table}[tbh]
\caption{The different ontologies and graphs of SNIK and their sources.
The namespace of each ontology is is equal to its URL with a slash suffix.
The graph group URL has no associated ontology and is the entry point of the RDF browser.
%All graphs are combined in the graph group \lowercase{\url{http://www.snik.eu/ontology}}.
}
\label{tab:source}
\begin{center}
%\begin{tabular}{\columnwidth}{lll}
\begin{tabular}{lll}
\toprule
\textbf{Prefix}	&\textbf{Ontology and Graph URL}			&\textbf{Source}\\		
\midrule
meta			&\url{http://www.snik.eu/ontology/meta}		&Meta Model\\
bb				&\url{http://www.snik.eu/ontology/bb}		&Textbook~\cite{bb}\\
ob				&\url{http://www.snik.eu/ontology/ob}		&Textbook~\cite{ob}\\
he				&\url{http://www.snik.eu/ontology/he}		&Textbook~\cite{he}\\
ciox			&\url{http://www.snik.eu/ontology/ciox}		&CIO Interview\\
it4it			&\url{http://www.snik.eu/ontology/it4it}	&Standard~\cite{it4it}\\
\midrule
sniko			&\url{http://www.snik.eu/ontology}			&Combined Graph Group\\
\bottomrule
\end{tabular}
\end{center}
\end{table}

\section{Methods}
\iffalse
\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\columnwidth]{img/hierarchy.pdf}
    \caption{Excerpt of the SNIK class hierarchy. Source: \cite{snikposter}.}
	\label{fig:hierarchy}
\end{figure}
\fi
\vspace{-3pt}
In order to specify, which information should be extracted from the books and to facilitate comparisons, we use a common data model.
Because processed textbooks contain abstract knowledge instead of information about any specific hospital, all concepts are modelled as classes.
We thus call our data model the \enquote{meta model} in accordance with the term's definition as a shared modelling language~\citep[p.~8]{ob}.
The meta model (see \cref{fig:metamodel}) provides a common vocabulary for the domain of HIS management and thus defines, which superclasses and properties can be used.
SNIK version \snikversionlink{} comprises five subontologies that are built upon the meta model, see Table 1.
%At the head of the class hierarchy (see \cref{fig:hierarchy}) is the \enquote{Top} class, which has exactly three disjunctive subclasses.
At the head of the class hierarchy is the \enquote{Top} class, which has exactly three disjunctive subclasses.
%
Following the meta model, each class has to be a subclass of exactly one of them.
The correct superclass of a new concept can be found by answering the question: Who (\enquote{Role}) does what (\enquote{Function}) and which information (\enquote{EntityType}) is needed? If a concept is neither of them, it cannot be modeled using the meta model.
As the subclass relation is transitive, a new class can be placed further down the hierarchy and it can still be inferred, whether it is a Function, Role or EntityType (see Figure 3).
Besides the subclass relationship, two classes can be connected with relations provided by the meta model.
The generic \enquote{is associated with} relationship carries little information.
For example, a role and a function can be connected as \enquote{is involved in} \enquote{is responsible for} and \enquote{approves}.
Relations that are neither of them can either be modeled by using the generic \enquote{is associated with} relation or by creating and using a new sub relation of \enquote{is associated with}
%
As a concession to practicality, we express each geleral rule extracted from a textbook as a single triple using classes as subject and object, and a property of the meta model.
For example, the rule "the CEO is involved in project reviews" is modelled as \enquote{\texttt{:Ceo} \aurl{meta}{isInvolvedIn} \texttt{:ProjectReview}.}, where \texttt{:Ceo} is a subclass of \aurl{meta}{Role} and \aurl{meta}{ProjectReview} is a subclass of \aurl{meta}{Function}.
While an OWL restrictions using \aurl{owl}{someValuesFrom} and \aurl{owl}{allValuesFrom} would be technically correct, the knowledge is not expressed that specifically in the textbooks.
Additionally, encoding each fact as a single triple facilitates tool support and prevents inconsistencies through non-atomic changes.

@@

\begin{table}
\caption{Access Options and Details.%
%KBox usage example: \texttt{pip install kbox \&\& kbox -kb http://www.snik.eu/ontology -install -server}.%doesn't work right now
}
\label{tab:access}
\begin{tabulary}{\columnwidth}{lL}
\toprule
URL						&\url{http://www.snik.eu/ontology}\\
Version					&\snikversionlink{}\\
%License					&CC BY-NC-SA 4.0\\
License					&Attribution-NonCommercial-ShareAlike 4.0 International (\href{https://creativecommons.org/licenses/by-nc-sa/4.0/}{CC BY-NC-SA 4.0})\\
Documentation	&\url{https://snikproject.github.io/ontology/}\\
SPARQL Endpoint			&\url{http://www.snik.eu/sparql}\\
LOD Cloud				&\url{https://lod-cloud.net/dataset/snik}\\
%Datahub				&\url{https://datahub.io/imise/snik/v/1}\\%offline
%Docker
KBox~\cite{kbox} Graph	&\url{http://www.snik.eu/ontology}\\
RDF Browser				&\url{http://www.snik.eu/ontology}\\
Visualization			&\url{http://www.snik.eu/graph}\\
Download				&\url{https://github.com/snikproject/ontology/archive/refs/tags/\snikversion.zip}\\
Figshare				&\url{https://doi.org/10.6084/m9.figshare.17057084.v1}\\
\bottomrule
\end{tabulary}%The source code for the services is available at \url{https://github.com/imise}
\end{table}

\iffalse
\begin{table}
\caption{Statistics}
\label{tab:statistics}
\centering
\begin{tabulary}{\columnwidth}{lS}
\toprule
\textbf{Category}					&\textbf{Count}\\
\midrule
Triples								&\sniktriples{}\\
Classes								&\snikclasses{}\\
Properties							&\snikproperties{}\\
Internal Links						&360\\
Links to HITO~\citep{hitometh2}  	&260\\
Links to DBpedia~\citep{dbpedia} 	&\sniklinks{}\\
%Subontologies	&\url{http://www.snik.eu/ontology/bb}\\
%		&\url{http://www.snik.eu/ontology/ciox,}\\
%		&\url{http://www.snik.eu/ontology/ob}\\
%		&\url{http://www.snik.eu/ontology/he}\\
%		&\url{http://www.snik.eu/ontology/it4it}\\
\bottomrule
\end{tabulary}%The source code for the services is available at \url{https://github.com/imise}
\end{table}
\fi

\begin{figure*}
\caption{The SNIK meta model}
\label{fig:metamodel}
\centering
%\includegraphics[width=0.9\textwidth]{img/metamodel9s.pdf}%7 page version
\includegraphics[width=0.7\textwidth]{img/metamodel9s.pdf}
\end{figure*}

@@

%\section{Data Transformation Process}
%\subsection{Interlinking}
%As shown in \cref{...}, we aligned our dataset to several others:
%We manually aligned our dataset to HITO, the Health IT Ontology~\citep{hitometh2}
%We automatically aligned our dataset to:
%- DBpedia~\citep{dbpedia}, as  
%- 
%\section{Lifecycle}\label{sec:application}
\section{Results}\label{sec:application}
\iffalse
\begin{figure}[ht]
\caption{The SNIK lifecycle}
\label{fig:lifecycle}
\includegraphics[width=0.5\columnwidth]{cycle.pdf}
\end{figure}
\fi
When we add a new textbook to SNIK, we identify all concepts that fit the meta model and their relations to other concepts.
Some project members are not proficient in RDF serializations, so we first fill out a meta model conforming spreadsheet template.
We then use Tarql\footnote{\url{https://github.com/cygri/tarql}} with a mapping configuration file\footnote{\url{https://github.com/snikproject/snik-csv2rdf}} to convert that spreadsheet to RDF.
Next, we refine the data in Protégé and upload it to a Virtuso SPARQL endpoint.
%After the initial publish phase, we describe the repeating steps of the reuse phrase with the SNIK lifecycle in \Cref{fig:lifecycle}:
\begin{enumerate}
\item the Virtuoso SPARQL endpoint is used for querying and as data source for all our applications  
\item an instance of the OntoWiki~\citep{ontowiki} is used for punctual changes and additions by non-Semantic-Web-experts, supplemented by SPARUL for changes involving large numbers of classes 
\item LIMES~\citep{limes} generates interlink candidates between the different textbooks, which can be approved or rejected by the users.
\aurl{skos}{closeMatch} is used instead of \aurl{owl}{equivalentClass} to emphasize that not only the names of concepts may differ between textbooks but there may be subtle differences in meaning as well.
We do not intent to express different treatment, such as reasoning, due to the theoretical difference between \aurl{skos}{Concept} and \aurl{owl}{Class}.
Links to HITO and DBpedia are created as well.%, see \cref{tab:statistics}.
\item LodView\footnote{\url{https://lodview.it/}} lets the user browse among the classes of SNIK and view particular classes in detail
\item SNIK Graph, detailed in \Cref{sec:snik-graph}, supplements the RDF browser by visualizing the relationships between classes.
Users often discover incorrect modelling or possibilities for enhancement in SNIK graph.
\item SNIK quality is a web application that uses SPARQL queries to find problems of varying degree, such as violations of domain, range or naming conventions, subclass cycles or missing definitions.
\item Problems suggested by users and SNIK quality are verified, solved, and published on the SPARQL endpoint using SPARUL queries, at which point the circle begins anew.
\end{enumerate}

%After the initial extraction step, SNIK is published and users suggest problems or enhancements.%Besides issues of collaborative editing, this required a regular export and reupload, which delayed the effect of changes in SNIK to the user facing applications.
%- git repository (link): collaborative editing but protege can cause large diffs -> people who understand rdf enough to use text editor ttl/rdfxml 
%- use ontowiki: slow but user friendly, undo function,
%- SPARUL queries
The technical environment of those services is described in~\citet{sniktec}.
Selected applications are described in the following.

%\section{Applications}
SNIK was initially intended~\citep{domaene} both as  software to support hospital CIOs and to support teaching.
For the former goal, two applications were designed and implemented as prototypes~\citep{toreonto}: (1) the requirements engineering decision support system TOREOnto and (2) the knowledge exploration and navigation visualization CIONx.
Due to internal regulations, efforts to integrate them into the informational infrastructure of the Uniklinikum Leipzig were stopped.
Consequently, the other approaches are in the area of teaching support.

%\subsection{Reuse of Standard Components}
%To focus the software development effort on the components described below, we reuse standard components for common use cases:
%Virtuoso Opensource 7 serves as the SPARQL endpoint.

\subsection{SNIK Graph}\label{sec:snik-graph}
%TODO: Search auto complete and suggestions
%\paragraperformance

Graph-based visualizations allow teachers to intuitively convey relationships between a selection of those concepts and also allow students to explore the domain on their own~\cite{ontologybased}.
There are several existing graph-based Linked Data visualizations~\cite{linkeddatavisualization}, which visualize RDF resources (classes or instanes) as nodes and their relationships as edges, but they do not fit the requirements we have previously identified regarding performance, maintenance, usability, functionality and up-to-dateness~\cite{visualizationoflargeontologies}.
SNIK Graph is a web-based client-side open source web application\footnote{Published at \url{http://www.snik.eu/graph}.} that offers Linked Data visualization for both classes and instances and according to the requirements of SNIK and its users.
With the thousands of classes of SNIK, graph-based visualization suffers from overplotting.
Thus, SNIK Graph offers several options to select and layout subgraphs, for example to show only a specific chapter of a book to prepare a lecture about a specific topic.
Users can also iteratively explore SNIK starting at a single class using neighbourhood and path operations. %(see \cref{fig:snik-graph-circle-star})

\paragraph{Design Goals and Requirements}
Our main goal is to visualize knowledge extracted from text books to users that may not have any Semantic Web experience.
The time and cognitive load of the users required to install, learn and operate the application should be as low as possible, so that they can focus on the data at hand and experience a benefit compared to only reading the textbook, such as when studying for an exam.
A web application is easiest to set up for the user, as it is operating system agnostic and does not need to be installed.

\paragraph{Implementation and Setup}
As none of the investigated existing approaches support all our use cases and design goals and provide adequate performance on more than 4000 nodes, we implemented SNIK Graph as a web application using JavaScript (EcmaScript 2015) based on the graph visualization library Cytoscape.js~\cite{cytoscape}.
SNIK Graph is freely available as open source software\footnote{Git repository at \url{https://github.com/snikproject/snik-graph}, licensed under CC BY-NC-SA 4.0}.
As a client-side tool\footnotemark{}, SNIK Graph can be adapted to other knowledge bases and ontologies and published on any HTML web server by cloning the repository, installing the NPM dependencies and adapting the configuration file settings including the SPARQL endpoint URL.
\footnotetext{Aside from a SPARQL endpoint.}%
An installation containing SNIK is published at \url{https://www.snik.eu/graph}.

%\paragraph{Features}
\paragraph{Tabs and Containers}
%\begin{figure}[h]
%    \centering
%    \includegraphics[width=0.5\columnwidth]{img/tabs.png}
%    \caption{A session containing the default view and freely partitioned subgraphs containers.}
%	\label{fig:tabs}
%\end{figure}
%\vspace{-3pt}

%For this subgraphs of the ontology have to be extracted and organized.
%A feature of SNIK Graph, tabs, allows multi-instance usage.
%One major issue in working with SNIK Graph was the missing ability of organizing teaching scenarios.
To organize teaching scenarios, independent SNIK Graph instances are loaded into containers\footnotemark{} that can be organized around the browser window.
\footnotetext{Implemented using the JavaScript GoldenLayout framework (\url{https://golden-layout.com/}).} 
These containers can either be accessed as tabs or freely partitioned.% see \cref{fig:tabs}.
The content and of the all containers can be saved and loaded as a session to continue developing a teaching scenario at a later point.

%This feature allows better workflows in preparation and presentation of teaching scenarios.
%We use JSON formatted files for export and import.

\paragraph{Compound Layout}
%\begin{figure}[h]
%    \centering
%    \includegraphics[width=0.5\columnwidth]{img/combine.pdf}
%    \caption{Grouping of equivalent concepts from different sources in SNIK Graph (color coded).}% using the \enquote{combine matches} option.}
%	\label{fig:combine}
%\end{figure}
%\vspace{-3pt}

%\noindent For citations of references, we prefer the use of square brackets and consecutive numbers, e.g. as shown by Author et al. [2], [3, pp. 5–10], as mentioned earlier [1], [3], [9]. The following bibliography provides the basic formats as a reference list with entries for journal articles [1], book chapter [2], as well as a URL [5]. For further guidance please refer to the \href{https://ieeeauthorcenter.ieee.org/wp-content/uploads/IEEE-Reference-Guide.pdf}{IEEE-Reference-Guide}.

Users can group interlinked nodes together and either display them side by side or on top of each other.%, see \cref{fig:combine}.
As SNIK consists of more than 4000 classes, viewing large parts of it at once does not convey much information.%, see \cref{fig:much}.
To alleviate this, SNIK offers multiple exploration methods described in the following.
%\begin{figure}[h!]
%    \centering
%    \includegraphics[width=\linewidth]{much.pdf}
%    \caption{Excerpt of SNIK using the default force directed layout.}\label{fig:much}
%\end{figure}

\paragraph{Role Use}

%\todo{konrad an alle: was mache ich mit der sparql query? rausschmeissen, drin lassen oder umbauen? TP: drinlassen, aber direkt ans Bild hängen.. Sowas wie aus der Query folgt dieses Bild. Ich finde sowas sollte schon rein ins Paper}
%\begin{figure}[h]
%\begin{lstlisting}
%SELECT DISTINCT ?inner ?middle ?outer ?outerx {
% <role> (rdfs:subClassOf|skos:closeMatch|^skos:closeMatch)* ?inner.
% ?inner meta:subTopClass meta:Role.
% OPTIONAL {
%  ?inner ?p ?middle.
%  ?middle meta:subTopClass meta:Function.
%  OPTIONAL {
%   ?middle ?q ?outer.
%   ?outer meta:subTopClass meta:EntityType.
%   OPTIONAL {?outer (skos:closeMatch|^skos:closeMatch|^rdfs:subClassOf)+ ?outerx.}
%}}}
%\end{lstlisting}
%\caption{SPARQL query to generate the \emph{class use} visualization.}
%\label{lst:roleuse}
%\end{figure}
%\vspace{-3pt}

A frequent question is, what a given role does and which information is needed for those functions represented by the entity types connected to those functions.
This question is visually answered by the \enquote{role use} feature, which arranges roles, functions and entity types in concentric circles.%, see \Cref{fig:classuse}:

\begin{enumerate}%[align=left, labelwidth=1ex]
\item The first ring consists of the given role and all roles that are connected by a path of \aurl{rdfs}{subClassOf} and \aurl{skos}{closeMatch} edges.
\item The function ring consists of all functions adjacent to roles in the inner ring.
\item The third ring consists of all entity types adjacent to functions in the middle ring.
\item The final ring consists of all entity types that are connected to entity types from the third ring by a path of \aurl{skos}{closeMatch} and reverse \aurl{rdfs}{subClassOf} edges.
\end{enumerate}

\iffalse
\begin{figure}[h!]
    \centering
    \includegraphics[width=0.5\columnwidth]{img/class-use-project-manager.pdf}
    \caption{\emph{Role Use} of \aurl{bb}{ProjectManager}. Outermost layer ommitted due to space limitiations.}\label{fig:classuse}
\end{figure}
\fi

In SNIK Graph, this operation is called \emph{class use} and allows users to also put a function or entity type in the center.

%\section{Approach}
%Due to its large size, visualizing all of SNIK at once  overplotting.
%At the core of SNIK Graph is incremental exploration, which starts at one or more nodes and gradually expands them to related ones.

>>>>

%\pretitle{Pretitle}
\title{SNIK Quiz: Automatic Generation of Multiple Choice Questionnaires about Information Management in Hospitals}
%\thanks{This work is supported by the DFG (German Research Foundation) under the Project SNIK, Grant no. 1605/7-1 and 1387/8-1.}%bug: will create an empty first page

@@

\author[A]{\fnms{Konrad} \snm{Höffner}%
%\thanks{Corresponding author: Konrad Höffner, Institute for Medical Informatics, Statistics and Epidemiology, Leipzig University,
\thanks{Corresponding author: Konrad Höffner, IMISE, Leipzig University,
Härtelstraße 16--18, 04107 Leipzig, Germany; E-mail: konrad.hoeffner@imise.uni-leipzig.de.}},
\author[A]{\fnms{Arne} \snm{Roszeitis}},
\author[A]{\fnms{Max Niclas} \snm{Wächtler}},
\author[A]{\fnms{Franziska} \snm{Jahn}},
\author[A]{\fnms{Alfred} \snm{Winter}}
\runningauthor{K. Höffner et al.}
%\address[A]{Institute for Medical Informatics, Statistics and Epidemiology (IMISE), Leipzig University, Germany}
%\address[A]{Institute for Medical Informatics, Statistics and Epidemiology, Leipzig University, Germany}
\address[A]{IMISE, Leipzig University, Germany}
%Medical Informatics, Management of Health Information Systemsi
%Härtelstraße 16--18, D-04107 Leipzig

\iffalse
\author{\IEEEauthorblockN{Konrad Höffner}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-7358-3217}}
\and
\IEEEauthorblockN{Franziska Jahn}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0002-7687-8544}}
\and
\and
\IEEEauthorblockN{Alfred Winter}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
%alfred.winter@imise.uni-leipzig.de}
\url{https://orcid.org/0000-0003-0179-954X}}
\and
\IEEEauthorblockN{Thomas Pause}
\IEEEauthorblockA{\textit{Institute for Medical Informatics, Statistics and Epidemiology} \\
\textit{Leipzig University}\\
Leipzig, Germany \\
\url{https://orcid.org/0000-0001-5832-4890}}
}
\fi
\begin{abstract}
%Textbooks contain abstract knowledge about a domain.
%Textbooks about information management in hospitals describe the planning, monitoring and directing of a hospital's information system.

SNIK consists of the manually transformed content of three textbooks as Linked Open Data.
SNIK Quiz...
%The data model describes information management functions, roles executing these functions and the information used or updated by these functions.

%SNIK provides applications that are used to teach students internationally.
%and the result of applying the data model to three textbooks, an interview and a standard.
%To compare, 
%, making it a natural fit for RDF, RDFS and OWL.
%As the domain is large and highly relevant to students of Medical Informatics, modelling the knowledge is not only possible but also very useful.
%We publish the result over several interfaces that are useful for researchers, administrators or students, depending on their objectives and capabilities.
\end{abstract}

@@

\section{Introduction}
%A health information system (HIS) is the socio-technical subsystem of a care delivery organization~\citep{bb}.
%This includes its different application systems, computers, and network components as well as their users.
Medical informatics students, who are trained for executive positions in information management departments of healthcare institutions, such as hospitals, need a clear terminology of their domain.
This terminology is offered by SNIK~\citep{semantischesnetz,sniktec}, the Semantic Network of Information Management in Hospitals (\enquote{Krankenhaus} in German), which integrates knowledge extracted from three textbooks~\citep{bb,ob,he} in the form of Linked Open Data.

%A HIS processes data, information, and knowledge and its management involves planning, monitoring and directing those activities.
%Due to the complexity and the unique conditions in health care, HIS management is an challenging task.
%There are many different frameworks, textbooks and articles describing the scope of HIS management from the perspective of medical informatics.
%However, the disciplines of business informatics and information systems (IS) provide an even broader view on information systems and their management.
%A structured representation of the different perspectives leads to a holistic view on HIS management and helps help researchers and students connect their existing knowledge with further knowledge from other sources during research and learning.
%three textbooks~\citep{bb,ob,he} and other sources, see \cref{tab:source}.
%\section{Sources}\label{sec:sources}
%Three textbooks provide different views on the domain of Hospital Information Management:
%\citet{bb} presents a broad view on \enquote{typical architectures of health information systems and their systematic strategic management}.
%\citep{ob} concentrates on the \emph{tactical} management of information systems in general and on healthcare in particular.
%The focus of tactical management lies on the planning and operation of projects.
%\citet{he} explains information management beyond the scope of healthcare.
%Other sources are interviews and standards.
%CIOX is based on an interview with the CIO of the Universitätsklinikum Leipzig.
%IT4IT is based on the IT4IT standard.\todo{Sebastian: Was über Standards und IT4IT schreiben}
%
%We discuss advantages and disadvantages of the interfaces and give recommendations on which ones present the best compromise for different use cases and target audiences.
%We conclude with plans for future work on interlinking and visualization.
%As the domain is large and highly relevant to students of Medical Informatics, modelling the knowledge is not only possible but also very useful.
%Due to different frameworks and textbooks dealing with information management in healthcare, modelling the knowledge unravels the links between the different views on information management.
%These are only implicitly known or not known at all by experts in the field.
%
%
%Publishing textbook knowledge as Linked Data enables different ways of teaching.
%The data is continously revised: users constantly report wrong or missing data in the visualization, which is then corrected, respectively revised, by the researchers of the project.

\iffalse
\begin{table}[tbh]
\caption{The different ontologies and graphs of SNIK and their sources.
The namespace of each ontology is is equal to its URL with a slash suffix.
The graph group URL has no associated ontology and is the entry point of the RDF browser.
%All graphs are combined in the graph group \lowercase{\url{http://www.snik.eu/ontology}}.
}
\label{tab:source}
\begin{center}
%\begin{tabular}{\columnwidth}{lll}
\begin{tabular}{lll}
\toprule
\textbf{Prefix}	&\textbf{Ontology and Graph URL}			&\textbf{Source}\\		
\midrule
meta			&\url{http://www.snik.eu/ontology/meta}		&Meta Model\\
bb				&\url{http://www.snik.eu/ontology/bb}		&Textbook~\cite{bb}\\
ob				&\url{http://www.snik.eu/ontology/ob}		&Textbook~\cite{ob}\\
he				&\url{http://www.snik.eu/ontology/he}		&Textbook~\cite{he}\\
ciox			&\url{http://www.snik.eu/ontology/ciox}		&CIO Interview\\
it4it			&\url{http://www.snik.eu/ontology/it4it}	&Standard~\cite{it4it}\\
\midrule
sniko			&\url{http://www.snik.eu/ontology}			&Combined Graph Group\\
\bottomrule
\end{tabular}
\end{center}
\end{table}
\fi

\section{Methods}

\begin{figure*}
\caption{The SNIK meta model}
\label{fig:metamodel}
\centering
\includegraphics[width=0.7\textwidth]{img/metamodel9s.pdf}
\end{figure*}

\iffalse
\begin{figure}[h]
    \centering
    \includegraphics[width=0.5\columnwidth]{img/hierarchy.pdf}
    \caption{Excerpt of the SNIK class hierarchy. Source: \cite{snikposter}.}
	\label{fig:hierarchy}
\end{figure}
\vspace{-3pt}
\fi

SNIK describes information management functions, roles executing these functions and entity types, the information used or updated by these functions.
Because the textbooks describe those concepts in the abstract sense, and not those of any concrete hospital, those entities are modelled as classes and individuals at the same time, using OWL 2 DL \emph{punning}.
Thus, \emph{function}, \emph{role} and \emph{entity type} are metaclasses and the ontology of SNIK is called the \emph{meta model}, see \cref{fig:metamodel}.
%In order to specify, which information should be extracted from the books and to facilitate comparisons, we use a common data model.
%Because processed textbooks contain abstract knowledge instead of information about any specific hospital, all concepts are modelled as classes.
%We thus call our data model the \enquote{meta model} in accordance with the term's definition as a shared modelling language~\citep[p.~8]{ob}.
%The meta model (see \cref{fig:metamodel}) provides a common vocabulary for the domain of HIS management and thus defines, which superclasses and properties can be used.
%SNIK version \snikversionlink{} comprises five subontologies that are built upon the meta model, see Table 1.
%At the head of the class hierarchy (see \cref{fig:hierarchy}) is the \enquote{Top} class, which has exactly three disjunctive subclasses.
%At the head of the class hierarchy is the \enquote{Top} class, which has exactly three disjunctive subclasses.
%
%Following the meta model, each class has to be a subclass of exactly one of them.
%The correct superclass of a new concept can be found by answering the question: Who (\enquote{Role}) does what (\enquote{Function}) and which information (\enquote{EntityType}) is needed? If a concept is neither of them, it cannot be modeled using the meta model.
%As the subclass relation is transitive, a new class can be placed further down the hierarchy and it can still be inferred, whether it is a Function, Role or EntityType (see Figure 3).
%Besides the subclass relationship, two classes can be connected with relations provided by the meta model.
%The generic \enquote{is associated with} relationship carries little information.
%For example, a role and a function can be connected as \enquote{is involved in} \enquote{is responsible for} and \enquote{approves}.
%Relations that are neither of them can either be modeled by using the generic \enquote{is associated with} relation or by creating and using a new sub relation of \enquote{is associated with}
%
%As a concession to practicality, we express each geleral rule extracted from a textbook as a single triple using classes as subject and object, and a property of the meta model.
%For example, the rule "the CEO is involved in project reviews" is modelled as \enquote{\texttt{:Ceo} \aurl{meta}{isInvolvedIn} \texttt{:ProjectReview}.}, where \texttt{:Ceo} is a subclass of \aurl{meta}{Role} and \aurl{meta}{ProjectReview} is a subclass of \aurl{meta}{Function}.
%While an OWL restrictions using \aurl{owl}{someValuesFrom} and \aurl{owl}{allValuesFrom} would be technically correct, the knowledge is not expressed that specifically in the textbooks.
%Additionally, encoding each fact as a single triple facilitates tool support and prevents inconsistencies through non-atomic changes.

@@

@@

%\section{Data Transformation Process}
%\subsection{Interlinking}
%As shown in \cref{...}, we aligned our dataset to several others:
%We manually aligned our dataset to HITO, the Health IT Ontology~\citep{hitometh2}
%We automatically aligned our dataset to:
%- DBpedia~\citep{dbpedia}, as  
%- 
%\section{Lifecycle}\label{sec:application}
%Virtuoso SPARQL endpoint is used for querying and as data source for all our applications

%After the initial extraction step, SNIK is published and users suggest problems or enhancements.%Besides issues of collaborative editing, this required a regular export and reupload, which delayed the effect of changes in SNIK to the user facing applications.
%- git repository (link): collaborative editing but protege can cause large diffs -> people who understand rdf enough to use text editor ttl/rdfxml 
%- use ontowiki: slow but user friendly, undo function,
%- SPARUL queries
%The technical environment of those services is described in~\citet{sniktec}.

%\section{Applications}
